Results

### 2024-09-13 scripts/Results.Rmd
species added to legend of leafplot

@@

ggplot(suitability_amounts,
       aes(x = Percent, y = Records, color = Species, group = Species)) +
  geom_line(lty = 1) +
  scale_color_grey(guide = 'none') + 
  ggnewscale::new_scale_color() +
  geom_ribbon(data = suitability_means, aes(ymin = lower, ymax = upper, x = Percent, fill = '95% CI'),
              inherit.aes = F, alpha = 0.5) + 
  geom_line(data = suitability_means, 
            aes(x = Percent, y =  mean, color = 'Mean (95% CI)'), 
            inherit.aes = F, lwd = 1) + 
  geom_line(data = suitability_means, aes(y = Percent/100, x = Null_mod, color = 'Theoretical Probability'),
            inherit.aes = F, lwd = 1) +
  geom_line(data = fp, aes(y = suitability, x = obs*100, color = 'Observed Populations'), inherit.aes = F, lwd = 1) +

  labs(
    title = 'Populations are found in areas\nwith higher predicted suitability',
    x = "Raster Cells (cumulative)",
    y = 'Predicted Suitability') + 
  theme_classic() +
  scale_y_continuous(
    breaks = seq(0, 1, by = 0.2)
  )  +
  scale_fill_manual(values = linecols, guide = 'none') + 
  scale_colour_manual(values = linecols, name = NULL) +

@@

  geom_label(data = labs, aes(x = x, y = y, label = label), 
             inherit.aes = F, size = 2.5,
             fill='transparent', color = 'white') +

  ######        USE THIS TO MAKE THE PLOT TRANSPARENT FOR THE TALK        #####

>>>>

## create a dummy species var to put the grey50 color on the legend. 
dum_species <- data.frame(Percent = 1, Records = 0.1, Species = 'dum')

@@

ggplot(suitability_amounts,
       aes(x = Percent, y = Records, color = Species, group = Species)) +
  geom_line(lty = 1) +
  scale_color_grey(guide = 'none') + 
  ggnewscale::new_scale_color() +
  geom_ribbon(data = suitability_means, aes(ymin = lower, ymax = upper, x = Percent, fill = '95% CI'),
              inherit.aes = F, alpha = 0.5) + 
  geom_line(data = suitability_means, 
            aes(x = Percent, y =  mean, color = 'Mean (95% CI)'), 
            inherit.aes = F, lwd = 1) + 
  geom_line(data = suitability_means, aes(y = Percent/100, x = Null_mod, color = 'Theoretical Probability'),
            inherit.aes = F, lwd = 1) +
  geom_line(data = fp, aes(y = suitability, x = obs*100, color = 'Observed Populations'), inherit.aes = F, lwd = 1) +
  geom_line(data = dum_species, aes(color = 'Species'), lwd = 1) +

  labs(
    title = 'Populations are found in areas\nwith higher predicted suitability',
    x = "Raster Cells (cumulative)",
    y = 'Predicted Suitability') + 
  theme_classic() +
  scale_y_continuous(
    breaks = seq(0, 1, by = 0.2)
  )  +
  scale_fill_manual(values = linecols, guide = 'none') + 
  scale_colour_manual(
    values = linecols, name = NULL, 
    breaks = c('Species', 'Mean (95% CI)', 'Theoretical Probability', 'Observed Populations')) +

@@

  geom_label(data = labs, aes(x = x, y = y, label = label), 
             inherit.aes = F, size = 2.5 ,

 ######        USE THIS TO MAKE THE PLOT TRANSPARENT FOR THE TALK        #####
             fill='transparent', color = 'white') +
